Gozde and Liora's Replication Code

### 2015-05-12 replication project.Rmd
Added note line 11

Note: Our regression values are slightly different from the authors as his stata code used a slightly different method than our function (glmmPQL) to calculate Penalized Quasi-likehood. Finally, we were unfortunately not able to reproduce the last two figures that showed the joint impact of more than 2 variables.

>>>>

Note: Our regression values are slightly different from the authors as his stata code used a slightly different method than our function (glmmPQL) to calculate Penalized Quasi-likehood. Finally, we were unfortunately not able to reproduce the last two figures that showed the joint impact of more than 2 variables.  These graphs are dependant on a concept called "covariate contributions" developed by Mitchell and Chen (2005), that represents the aggregation into a single quantity of individual effects of all independant variables that are not varied in a graph.  Graphs based on this concept were beyond the scope of our understanding or ability for this project.
